Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-11-27 article.tex
Expand intro

Compilation refers to the process of translating from one language to another, most often from a programming language intended for humans to work with, to machine-/bytecode intended to be executed on a target platform. This process can be divided into several distinct phases, which are grouped into one of two stages, colloquially referred to as the \textit{frontend} and \textit{backend}. The former translating a high-level programming language to an \textit{intermediate representation} (IR) layer and the latter translating IR to executable machine code on a target platform (e.g. x86, ARM) or bytecode for a target VM (e.g. JVM, CLR).

@@

  \draw [decorate,decoration={brace,amplitude=5pt,mirror,raise=4ex}]
    (0.3,-1) -- (0.3,1) node[midway,xshift=3em,rotate=-90]{Backend};
  \draw [decorate,decoration={brace,amplitude=5pt,mirror,raise=4ex}]
    (0.3,1.25) -- (0.3,3.25) node[midway,xshift=3em,rotate=-90]{Frontend};
\end{tikzpicture}}
\caption{Compiler phases, backend highlighted}
\end{figure}
A critical part of the backend stage is assigning each variable (also referred to as \textit{virtual}) of the source program to a physical register on the target processor.

>>>>

Compilation refers to the process of translating from one language to another, most often from a high-level programming language intended for humans to work with, to machine- or bytecode intended to be executed on a target platform. This process can be divided into several distinct phases, which are grouped into one of two stages colloquially referred to as the \textit{frontend} and \textit{backend}. The former translating a high-level programming language to an \textit{intermediate representation} (IR) layer and the latter translating IR to executable machine code on a target platform or bytecode for a target \textit{virtual machine} (VM).

@@

  \draw [decorate,decoration={brace,amplitude=5pt,mirror,raise=4ex}]
    (0.3,-1) -- (0.3,1) node[midway,xshift=3em,rotate=-90]{Backend};
  \draw [decorate,decoration={brace,amplitude=5pt,mirror,raise=4ex}]
    (0.3,1.25) -- (0.3,3.25) node[midway,xshift=3em,rotate=-90]{Frontend};
\end{tikzpicture}}
\caption{Compiler phases, backend highlighted}
\end{figure}
Most operations of a general-purpose programming language are translated to a set of logic,  control, and arithmetic processor instructions, that are intended to be executed sequentially on a computer processor: a single circuit/chip, referred to as the \textit{central processing unit} (CPU). CPU design varies and has evolved over time, but most processors executing logic operations are \textit{register machines}, in that they use a limited set of \textit{general-purpose registers} (GPRs) to store working values in combination with \textit{random access memory} (RAM) for mid-term and other I/O peripherals for long-term storage.

The reason for this can largely be attributed to performance, as register machines routinely outperform so-called stack machines \cite{ShiYunhe2008VmsS} that are often used in VMs.
Due to this, and the limited amount of GPRs available, a crucial part of the backend stage for an optimizing compiler is assigning each variable  of the source program to a GPR in such a way that maximizes performance without sacrificing correctness.

The process of assigning each variable to a GPR is generally referred to as \textit{register allocation}, and
